Appendix
========================================================

One-group design:

```{r}
## Set A
## Unifrm(0, 1)
# 1 group

con.int.a<-function(alpha,n,m){
  set.seed(45)
  est.var <- replicate(m,
                     {x <- runif(n)
                      tau<-sum(abs(x-median(x)))/n
                      delta<-(mean(x)-median(x))/tau
                      gamma<-var(x)/tau^2
                      #gamma<-1.23
                      (delta^2+gamma-1)/n})
  tau <- replicate(m,
                   {x <- runif(n)
                    sum(abs(x-median(x)))/n})
  
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var))
  return(exp(Y))
}

## see if it CIs cover true_tau


coverage.a<-function(alpha,n,m){
  true_tau<-sqrt((1/12)/1.33)
  
  ans<-con.int.a(alpha,n,m)
  L<-(ans[,1]<true_tau)*1
  U<-(ans[,2]>true_tau)*1
  count=L*U

  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}
#setA # n=10 # 

m=1000
a<-data.frame(n=10,alpha_0.1=coverage.a(0.1,10,m), alpha_0.05=coverage.a(0.05,10,m),alpha_0.01=coverage.a(0.01,10,m))
#set A #n=25 
b<-data.frame(n=25,alpha_0.1=coverage.a(0.1,25,m), alpha_0.05=coverage.a(0.05,25,m),alpha_0.01=coverage.a(0.01,25,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=coverage.a(0.1,50,m), alpha_0.05=coverage.a(0.05,50,m),alpha_0.01=coverage.a(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=coverage.a(0.1,200,m), alpha_0.05=coverage.a(0.05,200,m),alpha_0.01=coverage.a(0.01,200,m))
setA=rbind(a,b,c,d)

################ set B

con.int.b<-function(alpha,n,m){
  set.seed(45)
  est.var <- replicate(m,
                       {x <- rnorm(n, 0, 1)
                        tau<-sum(abs(x-median(x)))/n
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n})
  tau <- replicate(m,
                   {x <- rnorm(n, 0, 1)
                    sum(abs(x-median(x)))/n})
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var))
  return(exp(Y))
}

## true_tau


coverage.b<-function(alpha,n,m){
  true_tau<-sqrt(1/1.57)
  ans<-con.int.b(alpha,n,m)
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

#set B # n=10 # norm
m=1000
a<-data.frame(n=10,alpha_0.1=coverage.b(0.1,10,m), alpha_0.5=coverage.b(0.05,10,m),alpha_0.01=coverage.b(0.01,10,m))
#set B #n=25 # norm
b<-data.frame(n=25,alpha_0.1=coverage.b(0.1,25,m), alpha_0.5=coverage.b(0.05,25,m),alpha_0.01=coverage.b(0.01,25,m))
# set B # n=50 # norm
c<-data.frame(n=50,alpha_0.1=coverage.b(0.1,50,m), alpha_0.5=coverage.b(0.05,50,m),alpha_0.01=coverage.b(0.01,50,m))
# set B # n=200 # norm
d<-data.frame(n=200,alpha_0.1=coverage.b(0.1,200,m), alpha_0.5=coverage.b(0.05,200,m),alpha_0.01=coverage.b(0.01,200,m))

setB=rbind(a,b,c,d)

############ set C # t.distrbution

con.int.c<-function(alpha,n,m){
  set.seed(45)
  est.var <- replicate(m,
                       {x <- rt(n,5)
                        tau<-sum(abs(x-median(x)))/n
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n})
  tau <- replicate(m,
                   {x <- rt(n,5 )
                    sum(abs(x-median(x)))/n})
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var))
  return(exp(Y))
}

## true_tau


coverage.c<-function(alpha,n,m){
  true_tau<-sqrt((5/3)/2)
  ans<-con.int.c(alpha,n,m)
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )

}

#set C # n=10 # t.dist
m=1000
a<-data.frame(n=10,alpha_0.1=coverage.c(0.1,10,m), alpha_0.5=coverage.c(0.05,10,m),alpha_0.01=coverage.c(0.01,10,m))
#set C #n=25 #  t.dist
b<-data.frame(n=25,alpha_0.1=coverage.c(0.1,25,m), alpha_0.5=coverage.c(0.05,25,m),alpha_0.01=coverage.c(0.01,25,m))
# set c # n=50 # t.dist
c<-data.frame(n=50,alpha_0.1=coverage.c(0.1,50,m), alpha_0.5=coverage.c(0.05,50,m),alpha_0.01=coverage.c(0.01,50,m))
# set c # n=200 # t.dist
d<-data.frame(n=200,alpha_0.1=coverage.c(0.1,200,m), alpha_0.5=coverage.c(0.05,200,m),alpha_0.01=coverage.c(0.01,200,m))
setC=rbind(a,b,c,d)

########### set D # rgamma

con.int.d<-function(alpha,n,m){
  set.seed(45)
  est.var <- replicate(m,
                       {x <- rgamma(n,7,1)
                        tau<-sum(abs(x-median(x)))/n
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n})
  tau <- replicate(m,
                   {x <- rgamma(n,7,1)
                    sum(abs(x-median(x)))/n})
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var))
  return(exp(Y))
}

## true_tau


coverage.d<-function(alpha,n,m){
  true_tau<-sqrt(7/1.63)
  ans<-con.int.d(alpha,n,m)
  
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )

}

#set D # n=10 # rgamma
m=1000
a<-data.frame(n=10,alpha_0.1=coverage.d(0.1,10,m), alpha_0.05=coverage.d(0.05,10,m),alpha_0.01=coverage.d(0.01,10,m))
#set D #n=25 #  rgamma
b<-data.frame(n=25,alpha_0.1=coverage.d(0.1,25,m), alpha_0.05=coverage.d(0.05,25,m),alpha_0.01=coverage.d(0.01,25,m))
# set D # n=50 # rgamma
c<-data.frame(n=50,alpha_0.1=coverage.d(0.1,50,m), alpha_0.05=coverage.d(0.05,50,m),alpha_0.01=coverage.d(0.01,50,m))
# set D # n=200 # rgamma
d<-data.frame(n=200,alpha_0.1=coverage.d(0.1,200,m), alpha_0.05=coverage.d(0.05,200,m),alpha_0.01=coverage.d(0.01,200,m))
setD=rbind(a,b,c,d) 


## set E # chi-square(4)
con.int.e<-function(alpha,n,m){
  set.seed(45)
  est.var <- replicate(m,
                       {x <- rchisq(n,4)
                        tau<-sum(abs(x-median(x)))/n
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n})
  tau <- replicate(m,
                 {x <- rchisq(n,4)
                  sum(abs(x-median(x)))/n})
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var))
  return(exp(Y))
}

## true_tau
coverage.e<-function(alpha,n,m){
  true_tau<-sqrt((2*4)/1.81)
  ans<-con.int.e(alpha,n,m)
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

#set E # n=10 
m=1000
a<-data.frame(n=10, alpha_0.1=coverage.e(0.1,10,m), alpha_0.5=coverage.e(0.05,10,m),alpha_0.01=coverage.e(0.01,10,m))
#set E #n=25 
b<-data.frame(n=25, alpha_0.1=coverage.e(0.1,25,m), alpha_0.5=coverage.e(0.05,25,m),alpha_0.01=coverage.e(0.01,25,m))
# set E # n=50 
c<-data.frame(n=50, alpha_0.1=coverage.e(0.1,50,m), alpha_0.5=coverage.e(0.05,50,m),alpha_0.01=coverage.e(0.01,50,m))
# set E # n=200 
d<-data.frame(n=200, alpha_0.1=coverage.e(0.1,200,m), alpha_0.5=coverage.e(0.05,200,m),alpha_0.01=coverage.e(0.01,200,m))
setE=rbind(a,b,c,d)

```

Two-group design:

```{r}
## uniform and norm
con.int.ab<-function(alpha,n1,n2,m){
  set.seed(1990)
  est.var1 <- replicate(m,
                       {x <- runif(n1)
                        tau<-sum(abs(x-median(x)))/n1
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n1})
  tau1 <- replicate(m,
                      {x <- runif(n1)
                       sum(abs(x-median(x)))/n1})

  est.var2 <- replicate(m,
                       {x <- rnorm(n2, 0, 1)
                        tau<-sum(abs(x-median(x)))/n2
                        delta<-(mean(x)-median(x))/tau
                        gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n2})
  tau2 <- replicate(m,
                    {x <- rnorm(n2, 0, 1)
                     sum(abs(x-median(x)))/n2})
  coe<-qnorm(1-alpha/2)
  c1<-n1/(n1-1)
  c2<-n2/(n2-1)
                     
  Y<-cbind(log((c1*tau1)/(c2*tau2))-coe*sqrt(est.var1+est.var2), log((c1*tau1)/(c2*tau2))+coe*sqrt(est.var1+est.var2))
  return(exp(Y))
}


## true_tau
coverage.ab<-function(alpha,n1,n2,m){
  true_tau1<-sqrt((1/12)/1.33)
  true_tau2<-sqrt(1/1.57)
  true_tau=true_tau1/true_tau2
  ans<-con.int.ab(alpha,n1,n2,m)
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

#setA and B # n=10 

m=1000
a<-data.frame(n1=10, n2=10,alpha_0.1=coverage.ab(0.1,10,10,m), alpha_0.5=coverage.ab(0.05,10,10,m),alpha_0.01=coverage.ab(0.01,10,10,m))
b<-data.frame(n1=25, n2=10, alpha_0.1=coverage.ab(0.1,25,10,m), alpha_0.5=coverage.ab(0.05,25,10,m),alpha_0.01=coverage.ab(0.01,25,10,m))
c<-data.frame(n1=10, n2=25, alpha_0.1=coverage.ab(0.1,10,25,m), alpha_0.5=coverage.ab(0.05,10,25,m),alpha_0.01=coverage.ab(0.01,10,25,m))
d<-data.frame(n1=25, n2=25,alpha_0.1=coverage.ab(0.1,25,25,m), alpha_0.5=coverage.ab(0.05,25,25,m),alpha_0.01=coverage.ab(0.01,25,25,m))
e<-data.frame(n1=100,n2=100,alpha_0.1=coverage.ab(0.1,100,100,m), alpha_0.5=coverage.ab(0.05,100,100,m),alpha_0.01=coverage.ab(0.01,100,100,m))

setAB=rbind(a,b,c,d,e)


##########3 set B ans Set C (norm ,t-disttrbution)
con.int.bc<-function(alpha,n1,n2,m){
  set.seed(1990)
  est.var1 <- replicate(m,
                        {x <- rnorm(n1, 0, 1)
                         tau<-sum(abs(x-median(x)))/n1
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                         (delta^2+gamma-1)/n1})
  tau1 <- replicate(m,
                    {x <- rnorm(n1,0,1)
                     sum(abs(x-median(x)))/n1})
  est.var2 <- replicate(m,
                        {x <- rt(n2, 5)
                         tau<-sum(abs(x-median(x)))/n2
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                         (delta^2+gamma-1)/n2})
  tau2 <- replicate(m,
                    {x <- rt(n2, 5)
                     sum(abs(x-median(x)))/n2})
  coe<-qnorm(1-alpha/2)
  c1<-n1/(n1-1)
  c2<-n2/(n2-1)
  Y<-cbind(log((c1*tau1)/(c2*tau2))-coe*sqrt(est.var1+est.var2), log((c1*tau1)/(c2*tau2))+coe*sqrt(est.var1+est.var2))
  return(exp(Y))
}


## To see if CIS cover true_tau
coverage.bc<-function(alpha,n1,n2,m){
  true_tau1<-sqrt(1/1.57)
  true_tau2<-sqrt((5/3)/2)
  true_tau=true_tau1/true_tau2
  ans<-con.int.bc(alpha,n1,n2,m) 
  ## plug into the function to get confidence interval
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

#setB and C # n=10 # rnorm rbeta
m=1000
a<-data.frame(n1=10, n2=10,alpha_0.1=coverage.bc(0.1,10,10,m), alpha_0.5=coverage.bc(0.05,10,10,m),alpha_0.01=coverage.bc(0.01,10,10,m))
b<-data.frame(n1=25, n2=10,alpha_0.1=coverage.bc(0.1,25,10,m), alpha_0.5=coverage.bc(0.05,25,10,m),alpha_0.01=coverage.bc(0.01,25,10,m))
c<-data.frame(n1=10, n2=25,alpha_0.1=coverage.bc(0.1,10,25,m), alpha_0.5=coverage.bc(0.05,10,25,m),alpha_0.01=coverage.bc(0.01,10,25,m))
d<-data.frame(n1=25, n2=25,alpha_0.1=coverage.bc(0.1,25,25,m), alpha_0.5=coverage.bc(0.05,25,25,m),alpha_0.01=coverage.bc(0.01,25,25,m))
e<-data.frame(n1=100, n2=100,alpha_0.1=coverage.bc(0.1,100,100,m), alpha_0.5=coverage.bc(0.05,100,100,m),alpha_0.01=coverage.bc(0.01,100,100,m))
setBC=rbind(a,b,c,d,e)


##########3 set B and Set D (N(0,1) ,Gamma(7,1))
con.int.bd<-function(alpha,n1,n2,m){
  set.seed(1990)
  est.var1 <- replicate(m,
                        {x <- rnorm(n1, 0, 1)
                         tau<-sum(abs(x-median(x)))/n1
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                         (delta^2+gamma-1)/n1})
  tau1 <- replicate(m,
                    {x <- rnorm(n1,0,1)
                     sum(abs(x-median(x)))/n1})
  est.var2 <- replicate(m,
                        {x <- rgamma(n2, 7,1)
                         tau<-sum(abs(x-median(x)))/n2
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n2})
  tau2 <- replicate(m,
                    {x <- rgamma(n2, 7,1)
                    sum(abs(x-median(x)))/n2})
                    coe<-qnorm(1-alpha/2)
c1<-n1/(n1-1)
c2<-n2/(n2-1)
Y<-cbind(log((c1*tau1)/(c2*tau2))-coe*sqrt(est.var1+est.var2), log((c1*tau1)/(c2*tau2))+coe*sqrt(est.var1+est.var2))
return(exp(Y))
}


## To see if CIS cover true_tau
coverage.bd<-function(alpha,n1,n2,m){
  true_tau1<-sqrt(1/1.57)
  true_tau2<-sqrt(7/1.63)
  true_tau=true_tau1/true_tau2
  ans<-con.int.bd(alpha,n1,n2,m) ## Confidence Interval
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

#setB and D # n=10 # gamma and norm
m=1000
a<-data.frame(n1=10, n2=10,alpha_0.1=coverage.bd(0.1,10,10,m), alpha_0.5=coverage.bd(0.05,10,10,m),alpha_0.01=coverage.bd(0.01,10,10,m))
b<-data.frame(n1=25, n2=10,alpha_0.1=coverage.bd(0.1,25,10,m), alpha_0.5=coverage.bd(0.05,25,10,m),alpha_0.01=coverage.bd(0.01,25,10,m))
c<-data.frame(n1=10, n2=25,alpha_0.1=coverage.bd(0.1,10,25,m), alpha_0.5=coverage.bd(0.05,10,25,m),alpha_0.01=coverage.bd(0.01,10,25,m))
d<-data.frame(n1=25, n2=25,alpha_0.1=coverage.bd(0.1,25,25,m), alpha_0.5=coverage.bd(0.05,25,25,m),alpha_0.01=coverage.bd(0.01,25,25,m))
e<-data.frame(n1=100, n2=100,alpha_0.1=coverage.bd(0.1,100,100,m), alpha_0.5=coverage.bd(0.05,100,100,m),alpha_0.01=coverage.bd(0.01,100,100,m))
setBD=rbind(a,b,c,d,e)

##################SET D  Set E Gamma(7,1)& Chi-square(4)
con.int.de<-function(alpha,n1,n2,m){
  set.seed(1990)
  est.var1 <- replicate(m,
                        {x <- rgamma(n1, 7, 1)
                         tau<-sum(abs(x-median(x)))/n1
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                        (delta^2+gamma-1)/n1})
  tau1 <- replicate(m,
                    {x <- rgamma(n1, 7, 1)
                     sum(abs(x-median(x)))/n1})
  est.var2 <- replicate(m,
                        {x <- rchisq(n2, df=4)
                         tau<-sum(abs(x-median(x)))/n2
                         delta<-(mean(x)-median(x))/tau
                         gamma<-var(x)/tau^2
                         (delta^2+gamma-1)/n2})
  tau2 <- replicate(m,
                  {x <- rchisq(n2, df=4)
                   sum(abs(x-median(x)))/n2})
coe<-qnorm(1-alpha/2)
c1<-n1/(n1-1)
c2<-n2/(n2-1)
Y<-cbind(log((c1*tau1)/(c2*tau2))-coe*sqrt(est.var1+est.var2), log((c1*tau1)/(c2*tau2))+coe*sqrt(est.var1+est.var2))
return(exp(Y))
}


## To see if CIS cover true_tau
coverage.de<-function(alpha,n1,n2,m){
  true_tau1<-sqrt(7/1.63)
  true_tau2<-sqrt((2*4)/1.81)
  true_tau=true_tau1/true_tau2
  ans<-con.int.de(alpha,n1,n2,m) ## plug into the function to get confidence interval
  L<-(ans[,1]<=true_tau)*1
  U<-(ans[,2]>=true_tau)*1
  count=L*U
  p<-(sum(count)/m)
  se<-sqrt(p*(1-p)/m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5))
}

m=50000
a<-data.frame(n1=10, n2=10,alpha_0.1=coverage.de(0.1,10,10,m), alpha_0.05=coverage.de(0.05,10,10,m),alpha_0.01=coverage.de(0.01,10,10,m))
b<-data.frame(n1=25, n2=10,alpha_0.1=coverage.de(0.1,25,10,m), alpha_0.05=coverage.de(0.05,25,10,m),alpha_0.01=coverage.de(0.01,25,10,m))
c<-data.frame(n1=10, n2=25,alpha_0.1=coverage.de(0.1,10,25,m), alpha_0.05=coverage.de(0.05,10,25,m),alpha_0.01=coverage.de(0.01,10,25,m))
d<-data.frame(n1=25, n2=25,alpha_0.1=coverage.de(0.1,25,25,m), alpha_0.05=coverage.de(0.05,25,25,m),alpha_0.01=coverage.de(0.01,25,25,m))
e<-data.frame(n1=100, n2=100,alpha_0.1=coverage.de(0.1,100,100,m), alpha_0.05=coverage.de(0.05,100,100,m),alpha_0.01=coverage.de(0.01,100,100,m))
setDE=rbind(a,b,c,d,e)                
```

Table2 :
```{r}
setA;setB;setC;setD;setE
```

Table 3:
```{r}
setAB;setBC;setBD;setDE
```

Variance reduction: 

```{r}
## Set A
## uniform
# 1 group
####Vaiance reduction
con.int.a<-function(alpha,n,m){
  true_tau<-sqrt((1/12)/1.33)
  Y1<-matrix(rep(0,m), nrow=m/2); Y2<-matrix(rep(0,m), nrow=m/2)
  for (j in 1:(m/2)){
        u1<-runif(n)
        u2<-1-u1
        x1 <- qunif(u1, 0, 1)
        x2<-qunif(u2,0,1)
        tau1<-sum(abs(x1-median(x1)))/n 
        tau2<-sum(abs(x2-median(x2)))/n
        delta1<-(mean(x1)-median(x1))/tau1
        delta2<-(mean(x2)-median(x2))/tau2
        gamma1<-var(x1)/tau1^2
        gamma2<-var(x2)/tau2^2
        est.var1<-(delta1^2+gamma1-1)/n
        est.var2<-(delta2^2+gamma2-1)/n

  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y1[j,]<-exp(cbind(log(c*tau1)-coe*sqrt(est.var1), log(c*tau1)+coe*sqrt(est.var1)))
  Y2[j,]<-exp(cbind(log(c*tau2)-coe*sqrt(est.var2), log(c*tau2)+coe*sqrt(est.var2)))
  
}
  L1<-(Y1[,1]<true_tau)*1
  L2<-(Y2[,1]<true_tau)*1
  U1<-(Y1[,2]>true_tau)*1
  U2<-(Y2[,2]>true_tau)*1
  count1<-L1*U1
  count2<-L2*U2
  count=(count1+count2)/2
  p <- sum(count)/(m/2)
  se <-sd(count)/sqrt(m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

m=1000
a<-data.frame(n=10,alpha_0.1=con.int.a(0.1,10,m), alpha_0.05=con.int.a(0.05,10,m),alpha_0.01=con.int.a(0.01,10,m))
a#set A #n=25 
b<-data.frame(n=25,alpha_0.1=con.int.a(0.1,25,m), alpha_0.05=con.int.a(0.05,25,m),alpha_0.01=con.int.a(0.01,10,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=con.int.a(0.1,50,m), alpha_0.05=con.int.a(0.05,50,m),alpha_0.01=con.int.a(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=con.int.a(0.1,200,m), alpha_0.05=con.int.a(0.05,200,m),alpha_0.01=con.int.a(0.01,200,m))
vrsetA=rbind(a,b,c,d)
################set B
con.int.b<-function(alpha,n,m){
  true_tau<-sqrt(1/1.57)
  Y1<-matrix(rep(0,m), nrow=m/2); Y2<-matrix(rep(0,m), nrow=m/2)
  for (j in 1:(m/2)){
    u1<-runif(n)
    u2<-1-u1
    x1 <- qnorm(u1, 0, 1)
    x2<-qnorm(u2,0,1)
    tau1<-sum(abs(x1-median(x1)))/n 
    tau2<-sum(abs(x2-median(x2)))/n
    delta1<-(mean(x1)-median(x1))/tau1
    delta2<-(mean(x2)-median(x2))/tau2
    gamma1<-var(x1)/tau1^2
    gamma2<-var(x2)/tau2^2
    est.var1<-(delta1^2+gamma1-1)/n
    est.var2<-(delta2^2+gamma2-1)/n
    
    coe<-qnorm(1-alpha/2)
    c<-n/(n-1)
    Y1[j,]<-exp(cbind(log(c*tau1)-coe*sqrt(est.var1), log(c*tau1)+coe*sqrt(est.var1)))
    Y2[j,]<-exp(cbind(log(c*tau2)-coe*sqrt(est.var2), log(c*tau2)+coe*sqrt(est.var2)))
    
  }
  L1<-(Y1[,1]<true_tau)*1
  L2<-(Y2[,1]<true_tau)*1
  U1<-(Y1[,2]>true_tau)*1
  U2<-(Y2[,2]>true_tau)*1
  count1<-L1*U1
  count2<-L2*U2
  count=(count1+count2)/2
  p <- sum(count)/(m/2)
  se <-sd(count)/sqrt(m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

m=1000
a<-data.frame(n=10,alpha_0.1=con.int.b(0.1,10,m), alpha_0.05=con.int.b(0.05,10,m),alpha_0.01=con.int.b(0.01,10,m))
a#set A #n=25 
b<-data.frame(n=25,alpha_0.1=con.int.b(0.1,25,m), alpha_0.05=con.int.b(0.05,25,m),alpha_0.01=con.int.b(0.01,10,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=con.int.b(0.1,50,m), alpha_0.05=con.int.b(0.05,50,m),alpha_0.01=con.int.b(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=con.int.b(0.1,200,m), alpha_0.05=con.int.b(0.05,200,m),alpha_0.01=con.int.b(0.01,200,m))
vrsetB=rbind(a,b,c,d)
############ set C # t.distrbution

con.int.c<-function(alpha,n,m){
  true_tau<-sqrt((5/3)/2)
  Y1<-matrix(rep(0,m), nrow=m/2); Y2<-matrix(rep(0,m), nrow=m/2)
  for (j in 1:(m/2)){
    u1<-runif(n)
    u2<-1-u1
    x1 <- qt(u1, 5)
    x2<-qt(u2, 5)
    tau1<-sum(abs(x1-median(x1)))/n 
    tau2<-sum(abs(x2-median(x2)))/n
    delta1<-(mean(x1)-median(x1))/tau1
    delta2<-(mean(x2)-median(x2))/tau2
    gamma1<-var(x1)/tau1^2
    gamma2<-var(x2)/tau2^2
    est.var1<-(delta1^2+gamma1-1)/n
    est.var2<-(delta2^2+gamma2-1)/n
    
    coe<-qnorm(1-alpha/2)
    c<-n/(n-1)
    Y1[j,]<-exp(cbind(log(c*tau1)-coe*sqrt(est.var1), log(c*tau1)+coe*sqrt(est.var1)))
    Y2[j,]<-exp(cbind(log(c*tau2)-coe*sqrt(est.var2), log(c*tau2)+coe*sqrt(est.var2)))
    
  }
  L1<-(Y1[,1]<true_tau)*1
  L2<-(Y2[,1]<true_tau)*1
  U1<-(Y1[,2]>true_tau)*1
  U2<-(Y2[,2]>true_tau)*1
  count1<-L1*U1
  count2<-L2*U2
  count=(count1+count2)/2
  p <- sum(count)/(m/2)
  se <-sd(count)/sqrt(m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

m=1000
a<-data.frame(n=10,alpha_0.1=con.int.c(0.1,10,m), alpha_0.05=con.int.c(0.05,10,m),alpha_0.01=con.int.c(0.01,10,m))
#set A #n=25 
b<-data.frame(n=25,alpha_0.1=con.int.c(0.1,25,m), alpha_0.05=con.int.c(0.05,25,m),alpha_0.01=con.int.c(0.01,10,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=con.int.c(0.1,50,m), alpha_0.05=con.int.c(0.05,50,m),alpha_0.01=con.int.c(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=con.int.c(0.1,200,m), alpha_0.05=con.int.c(0.05,200,m),alpha_0.01=con.int.c(0.01,200,m))
vrsetC=rbind(a,b,c,d)

########### set D # rgamma
con.int.d<-function(alpha,n,m){
  true_tau<-sqrt(7/1.63)
  Y1<-matrix(rep(0,m), nrow=m/2); Y2<-matrix(rep(0,m), nrow=m/2)
  for (j in 1:(m/2)){
    u1<-runif(n)
    u2<-1-u1
    x1 <- qgamma(u1, 7, 1)
    x2<-qgamma(u2,7,1)
    tau1<-sum(abs(x1-median(x1)))/n 
    tau2<-sum(abs(x2-median(x2)))/n
    delta1<-(mean(x1)-median(x1))/tau1
    delta2<-(mean(x2)-median(x2))/tau2
    gamma1<-var(x1)/tau1^2
    gamma2<-var(x2)/tau2^2
    est.var1<-(delta1^2+gamma1-1)/n
    est.var2<-(delta2^2+gamma2-1)/n
    
    coe<-qnorm(1-alpha/2)
    c<-n/(n-1)
    Y1[j,]<-exp(cbind(log(c*tau1)-coe*sqrt(est.var1), log(c*tau1)+coe*sqrt(est.var1)))
    Y2[j,]<-exp(cbind(log(c*tau2)-coe*sqrt(est.var2), log(c*tau2)+coe*sqrt(est.var2)))
    
  }
  L1<-(Y1[,1]<true_tau)*1
  L2<-(Y2[,1]<true_tau)*1
  U1<-(Y1[,2]>true_tau)*1
  U2<-(Y2[,2]>true_tau)*1
  count1<-L1*U1
  count2<-L2*U2
  count=(count1+count2)/2
  p <- sum(count)/(m/2)
  se <-sd(count)/sqrt(m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

m=1000
a<-data.frame(n=10,alpha_0.1=con.int.d(0.1,10,m), alpha_0.05=con.int.d(0.05,10,m),alpha_0.01=con.int.d(0.01,10,m))
a#set A #n=25 
b<-data.frame(n=25,alpha_0.1=con.int.d(0.1,25,m), alpha_0.05=con.int.d(0.05,25,m),alpha_0.01=con.int.d(0.01,10,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=con.int.d(0.1,50,m), alpha_0.05=con.int.d(0.05,50,m),alpha_0.01=con.int.d(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=con.int.d(0.1,200,m), alpha_0.05=con.int.d(0.05,200,m),alpha_0.01=con.int.d(0.01,200,m))
vrsetD=rbind(a,b,c,d)
########## set E # Chi-square

con.int.e<-function(alpha,n,m){
  true_tau<-sqrt((2*4)/1.81)
  Y1<-matrix(rep(0,m), nrow=m/2); Y2<-matrix(rep(0,m), nrow=m/2)
  for (j in 1:(m/2)){
    u1<-runif(n)
    u2<-1-u1
    x1 <- qchisq(u1, 4)
    x2<-qchisq(u2, 4)
    tau1<-sum(abs(x1-median(x1)))/n 
    tau2<-sum(abs(x2-median(x2)))/n
    delta1<-(mean(x1)-median(x1))/tau1
    delta2<-(mean(x2)-median(x2))/tau2
    gamma1<-var(x1)/tau1^2
    gamma2<-var(x2)/tau2^2
    est.var1<-(delta1^2+gamma1-1)/n
    est.var2<-(delta2^2+gamma2-1)/n
    
    coe<-qnorm(1-alpha/2)
    c<-n/(n-1)
    Y1[j,]<-exp(cbind(log(c*tau1)-coe*sqrt(est.var1), log(c*tau1)+coe*sqrt(est.var1)))
    Y2[j,]<-exp(cbind(log(c*tau2)-coe*sqrt(est.var2), log(c*tau2)+coe*sqrt(est.var2)))
    
  }
  L1<-(Y1[,1]<true_tau)*1
  L2<-(Y2[,1]<true_tau)*1
  U1<-(Y1[,2]>true_tau)*1
  U2<-(Y2[,2]>true_tau)*1
  count1<-L1*U1
  count2<-L2*U2
  count=(count1+count2)/2
  p <- sum(count)/(m/2)
  se <-sd(count)/sqrt(m)
  rbind(Coverage.Prob=p*100, Standard.Error=round(se, digits=5) )
}

m=1000
a<-data.frame(n=10,alpha_0.1=con.int.e(0.1,10,m), alpha_0.05=con.int.e(0.05,10,m),alpha_0.01=con.int.e(0.01,10,m))
#set A #n=25 
b<-data.frame(n=25,alpha_0.1=con.int.e(0.1,25,m), alpha_0.05=con.int.e(0.05,25,m),alpha_0.01=con.int.e(0.01,10,m))
# setA # n=50 
c<-data.frame(n=50, alpha_0.1=con.int.e(0.1,50,m), alpha_0.05=con.int.e(0.05,50,m),alpha_0.01=con.int.e(0.01,50,m))
# set A n=200 
d<-data.frame(n=200,alpha_0.1=con.int.e(0.1,200,m), alpha_0.05=con.int.e(0.05,200,m),alpha_0.01=con.int.e(0.01,200,m))
vrsetE=rbind(a,b,c,d)

vrsetA;vrsetB;vrsetC;vrsetD;vrsetE
```

Importance Sampling for Chi-sqaure(4)
```{r}
vrunif<-function(alpha,n){
  true_tau<-sqrt((2*4)/1.81)
  ## proposed g(s)
  x<-rchisq(n,3.3)
  tau<-sum(abs(x-median(x)))/n
  delta<-(mean(x)-median(x))/tau
  gamma<-var(x)/tau^2

  est.var<-(delta^2+gamma-1)/n
  w<-exp(sum(dchisq(x,4,log=TRUE))-sum(dchisq(x,3.3,log=TRUE)))
   coe<-qnorm(1-alpha/2)
   c<-n/(n-1)
   Y<-exp(cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var)))

U<-1-(true_tau>Y[,2])*w
L<-1-(true_tau<Y[,1])*w
accept<-U*L
return(accept)
}
ant<-function(m, alpha,n){
  ans<-replicate(m, vrunif(alpha,n))
  p<-round(sum(ans)/m*100, digits=3)
  se<-round(sd(ans)/sqrt(m),digits=5)
  rbind(Prob=p,stanard.error=se)
}
cbind(ant(1000,0.1,10),ant(1000,0.05,10),ant(1000,0.01,10))
```

Control Variate for chi-square

```{r}
cvunif<-function(alpha,n){
  true_tau<-sqrt((2*4)/1.81)
  x<-rchisq(n,4)
  ss<-var(x)
  u<-mean(x)
  tau<-sum(abs(x-median(x)))/n
  delta<-(mean(x)-median(x))/tau
  gamma<-var(x)/tau^2
  est.var<-(delta^2+gamma-1)/n
  coe<-qnorm(1-alpha/2)
  c<-n/(n-1)
  Y<-exp(cbind(log(c*tau)-coe*sqrt(est.var), log(c*tau)+coe*sqrt(est.var)))
  
  U<-(true_tau<=Y[,2])
  L<-(true_tau>=Y[,1])
  accept<-U*L
  result<-c(accept,ss)
  return(result)
}

cv<-function(m, alpha,n){
  answ<-replicate(m, cvunif(alpha,n))
  a<-answ[1,]
  u<-answ[2,]
  model<-lm(a~u)
  beta1<--model$coefficients[2]
  ans<-a+beta1*(u-8)
  p<-round(sum(ans)/m*100, digits=3)
  se<-round(sd(ans)/sqrt(m),digits=5)
  rbind(p,se,summary(model)$r.squared)
}
cbind(cv(1000,0.1,10),cv(1000,0.05,10),cv(1000,0.01,10))
